Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-03 paper/ms.tex

\begin{figure*}[!t]
	%\gridline{
	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
	%}
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Positions of light curves from TESS Sectors 6
			and 7 in galactic coordinates.}
        Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
        target stars.  The target stars are mostly near the galactic
        plane.
		\label{fig:lcgalactic}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf  Zoom and coordinate transformation
			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
		The most populated cluster is XXX, primarily due to candidate
		members proposed by \citet{dias_proper_2014}.
		\label{fig:lcradeczoom}
	}
\end{figure}

@@

The on-sky locations of the light curves from Sectors 6 and 7
are shown in Figure~\ref{fig:lcgalactic}.
Black stars are the field stars for which we performed photometry,
but only to calibrate the cluster star sample.
The blue stars are the \numberlcs stars with light curves available
from \stscilink.
Most of the target stars are quite close to the galactic plane.
Gaps between CCD chips are also visible.

A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
for the Camera 1, Sector 6 field. The effects of galactic-latitude
dependent extinction are visible through the decreasing density of black
points towards the right of the image.
The highly clumped nature of the target stars is also apparent.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
TESS $T$-band magnitudes for the target stars.
Though most of the targets are faint, $\approx3\times10^4$ are
brighter than $T=13$, and so are more promising targets for any
detailed follow-up observtions.

@@

Our approach in this work is essentially identical to one of the methods 
described by \citet{hippke_wotan_2019}.
First, we run a generalized Lomb-Scargle periodogram on each TFA light 
curve \citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
If a peak is found with false alarm probability below $10^{-5}$, we consider 
the star ``variable'', and opt to 
detrend the light curve with robust penalized B-splines, which are splines 
with knot-length automatically determined via cross-validation 
\citep{eilers_flexible_1996}. The idea behind the cross-validation is that a 
larger  number of knots leads to smaller residuals on training data, but 
larger errors 
when tested on the entire dataset.
We used the \texttt{wotan} implementation, which is a wrapper to the 
\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from the fit 
residuals at each iteration 
\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.
The maximum number of spline knots is set to 50, which for each TESS sector 
($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm day}$ 
window.

@@

We then make a multi-page \texttt{.pdf} document report with the information 
necessary to make classifications for vetting.
These documents are released along with the light curves, and are a useful 
summary for anyone interested in the subset of objects that we have analyzed.
A full description of each page of the summary \texttt{.pdf} is given in the 
Appendix.

The classifications we used assessed:
\begin{enumerate}
    \item {\it Photometric variability classification}. Designations include 
    tags for planet candidates, eclipsing binaries, instrumental variations, 
    stellar variations, and ``weirdos''.
    %
    \item {\it Cluster membership status}. By default, all light curves were 
    made for stars with at least one literature claim of cluster membership.  
    However, some of these claims pre-dated the availability of Gaia-DR2
    parallaxes or proper motions.
    We therefore re-assess the membership status on a case-by-case basis 
    through inspection of the available astrometry and photometry.
    Known asterisms are also omitted at this point
    \citep[{\it e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
    %
    \item {\it Photometric blends}. Tags are created to highlight whether the 
    depth of the photometric signal shows a strong dependence on aperture 
    size, and also whether the in-transit minus the out-of-transit images 
    reveal that the source of variability is in fact far from the target star.
\end{enumerate}
The actual classifications were performed by LGB, JH, and JNW.
The \texttt{TagSpaces} software was used~--~an extremely helpful tool
for the purposes of easily assigning labels to documents.
An example vetting report for a planet candidate is described in
Appendix~\ref{appendix:vetreport}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Phased light curves for six of the \numberpcs candidate
    transiting planets identified in this work.}
    Black points are detrended flux measurements, phased to the
    best-fit orbital period indicated in the lower right of each
    panel.
    Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
    plotted with blue lines.
    For display purpses, a window of $\pm 4$ transit durations
    centered on the transit mid-point is displayed.
    The vetting reports for these objects are available at XXX.	%FIXME
    % TODO: include age? T mag?
    The Gaia source identifiers are
    a): 5605128927705695232, 
    b): 3125263468681400320, 
    c): 5510676828723793920, 
    d): 3007171311355035136, 
    e): 5617126180115568256, 
    f): 3220266049321724416.   
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

\subsection{Eclipsing binaries, stellar rotation}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{LS_period_vs_color_and_age.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Time evolution of Lomb-Scargle periodogram peak period versus
    Gaia color.}
    Red stars are on the right, blue stars are on the left.
    Each point on this diagram is a star for which the false alarm
    probability of the most powerful Lomb-Scargle peak is below
    $10^{-15}$.
    Additionally, we required (1) that the membership claim originate
    from \citet{cantat-gaudin_gaia_2018},
    \citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
    that the cluster with claimed membership had an age reported by
    \citet{Kharchenko_et_al_2013}.
	\label{fig:ls_peak_vs_time}
	}
\end{figure}

TODO: describe how this was made.
Figure~\ref{fig:ls_peak_vs_time}.

@@

Additional observations are needed for two major goals:
a) cluster membership confirmation
(age indicators, across the board);
b) verify the planetary nature of the signals
(seeing-limited photometry, RV mass measurement).

@@

@@

Lorem ipsum.

@@

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Positions of light curves from TESS Sectors 6
			and 7 in galactic coordinates.}
		Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
		target stars.  The target stars are mostly near the galactic
		plane.
		\label{fig:lcgalactic}
	}
\end{figure*}

%\begin{figure}[!t]
%	\begin{center}
%		\leavevmode
%		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
%	\end{center}
%	\vspace{-0.5cm}
%	\caption{
%		{\bf  Zoom and coordinate transformation
%			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
%		The most populated cluster is XXX, primarily due to candidate
%		members proposed by \citet{dias_proper_2014}.
%		\label{fig:lcradeczoom}
%	}
%\end{figure}

@@

The on-sky locations of the light curves from Sectors 6 and 7
are shown in Figure~\ref{fig:lcgalactic}.
Black stars are the field stars for which we performed photometry,
but only to calibrate the cluster star sample.
The blue stars are the \numberlcs stars with light curves available
from \stscilink.
Most of the target stars are quite close to the galactic plane.
Gaps between CCD chips are also visible.
The highly clumped nature of the target stars is also apparent.

%A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
%for the Camera 1, Sector 6 field. The effects of galactic-latitude
%dependent extinction are visible through the decreasing density of black
%points towards the right of the image.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
TESS $T$-band magnitudes for the target stars.
Though most of the targets are faint, $\approx3\times10^4$ are
brighter than $T=13$. These targets are more promising for any
detailed follow-up observtions.

@@

Our approach in this work is essentially identical to one of the
methods described by \citet{hippke_wotan_2019}.  First, before
sigma-clipping or omitting points near the edges of orbits we run a
generalized Lomb-Scargle periodogram on each TFA light curve
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
If a peak is found with false alarm probability below $10^{-5}$, we
consider the star ``variable'', and opt to detrend the light curve
with robust penalized B-splines, which are splines with knot-length
automatically determined via cross-validation
\citep{eilers_flexible_1996}. The idea behind the cross-validation is
that more knots leads to smaller residuals on training data, but
larger errors when tested on the entire dataset.  We used the
\texttt{wotan} implementation, which is a wrapper to the
\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
the fit residuals at each iteration
\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
number of spline knots is set to 50, which for each TESS sector
($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
day}$ window.

@@

We then make a multi-page \texttt{.pdf}-format document report with
the information necessary to make classifications for vetting.  These
vetting reports are released along with the light curves, and are a
useful summary for anyone interested in the subset of objects that we
have analyzed.  A full description of each page of the report is given
in Appendix~\ref{appendix:vetreport}.

The classifications we used assessed:
\begin{enumerate}
    \item {\it Photometric variability classification}. Designations
      include tags for planet candidates, eclipsing binaries,
      instrumental variations, stellar variations, and ``weirdos''.
    %
    \item {\it Cluster membership status}. By default, all light
      curves were made for stars with at least one literature claim of
      cluster membership.  However, some of these claims pre-dated the
      availability of Gaia-DR2 parallaxes or proper motions.  We
      therefore re-assess the membership status on a case-by-case
      basis through inspection of the available astrometry and
      photometry.  Known asterisms are also omitted at this point
      \citep[{\it
      e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
    %
    \item {\it Photometric blends}. Tags are created to highlight
      whether the depth of the photometric signal shows a strong
      dependence on aperture size, and also whether the in-transit
      minus the out-of-transit images reveal that the source of
      variability is in fact far from the target star.
\end{enumerate}
The initial classifications were performed by LGB, with subsequent
checking by JH and JNW.  The \texttt{TagSpaces} software was
used~--~an extremely helpful tool for the purposes of easily assigning
labels to documents.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
		{\bf Phased light curves for six of the \numberpcs candidate
			transiting planets identified in this work.}
		Black points are detrended flux measurements, phased to the
		best-fit orbital period indicated in the lower right of each
		panel.
		Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
		plotted with blue lines.
		For display purpses, a window of $\pm 4$ transit durations
		centered on the transit mid-point is displayed.
		The vetting reports for these objects are available at XXX.	%FIXME
		% TODO: include age? T mag?
		The Gaia source identifiers are
		a): 5605128927705695232, 
		b): 3125263468681400320, 
		c): 5510676828723793920, 
		d): 3007171311355035136, 
		e): 5617126180115568256, 
		f): 3220266049321724416.   
		\label{fig:ctoi_quilt}
	}
\end{figure*}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
		{\bf Time evolution of Lomb-Scargle periodogram peak period versus
			Gaia color.}
		Red stars are on the right, blue stars are on the left.
		Each point on this diagram is a star for which the false alarm
		probability of the most powerful Lomb-Scargle peak is below
		$10^{-15}$.
		Additionally, we required (1) that the membership claim originate
		from \citet{cantat-gaudin_gaia_2018},
		\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
		that the cluster with claimed membership had an age reported by
		\citet{Kharchenko_et_al_2013}.
		Our approach for avoiding photometric blends is described in
		\S~\ref{subsec:notplanets}.
		\label{fig:ls_peak_vs_time}
	}
\end{figure}

@@

\subsection{Eclipsing binaries, stellar rotation}
\label{subsec:notplanets}

To assess the prospects for studying forms of stellar variability
other than that caused by transiting planets, we performed a brief
additional exploration.
Using the Lomb-Scargle periodogram results from
\S~\ref{subsec:identifying_ctois}, we selected light curves 
for which the periodogram peak power had a corresponding false alarm
probability below $10^{-15}$.
We chose this cutoff to be small enough to give us a reasonable number
of objects, but large enough so that there would be no question that
the signal being detected was astrophysical.

Further, we then restricted our focus to stars with a cluster
membership claim in \citet{cantat-gaudin_gaia_2018},
\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}, since from our
experience these works have a relatively low false positive
probability.
We then further restricted our sample of stars to be those for which
the claimed cluster also had an age reported by
\citet{Kharchenko_et_al_2013}.

To remove obvious photometrically-blended duplicates, for any signal,
if any nearby stars had matching periods, we kept only the signal with
the lowest false alarm probabilty.
While this does not ensure that the detected signals originate from
the target star, it removed a large number of the duplicate signals,
and suits our exploratory purposes.

All told, this yielded 4057 stars between the ages of about 25 Myr and
1 Gyr.
In Figure~\ref{fig:ls_peak_vs_time}, we plot the Lomb-Scargle peak period
versus $G_{\rm Bp} - G_{\rm Rp}$ color over four different bins of
time.
The bins were chosen to match the sub-sample sizes within reasonable
proximity.

The youngest sample of stars is the reddest, as might be expected
given that many of these stars have not yet reached the main sequence,
and may exist along lines of sight with heavy extinction.

%FIXME
The weird part is that the oldest stars seem to have relatively more
sub-day peak periods.

@@

\subsection{The planet candidates require more observations}
Additional observations are needed for two major goals:
a) cluster membership confirmation
(age indicators, across the board);
b) verify the planetary nature of the signals
(seeing-limited photometry, RV mass measurement).

@@

\subsection{Eclipsing binary and stellar variability analyses may also
be feasible}

Lorem ipsum

@@

%FIXME: paraphrase / improve all the below
In this study, we made \numberlcs light curves of candidate young
stars, across \numberclusters distinct clusters.
Each light curve represents between 20 and 25 days of observations
of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.

In the process of making the light curves, we learned X, Y, and Z.
One point in particular was that image subtraction analyses seem to
do fine at detecting variability in the galactic plane.

In analyzing the noise properties of our light curves, we found that
at the faint end, contamination from unresolved background stars
dominated over other noise sources.

From a cursory transiting planet search, we identified \numberpcs
planet candidates, which need additional spectroscopic, photometric,
and imaging observations to verify (i) whether these candidates are
planets and (ii) whether the host stars are cluster members.
The vetting reports are available at \stscilink, and the planet
candidate parameters are on exoFOP-TESS.

We also briefly explored the age-evolution of extremely high-SNR
variability in the space of dominant period versus color
(Figure~\ref{fig:ls_peak_vs_time}).
This seems to show X, and Y.

The overall takeaway is that the sample of light curves and vetting
reports we have made should prove useful for doing some astrophysics.
%  We also comment on the possible utility of the light curve sample for
%  studies of stellar rotation evolution, and binary eccentricity
%  damping.

@@

\clearpage
\newpage
